---
pagetitle: "2024 Global Non-CO2 Report: MACC Curves "
output:
  html_document:
    number_sections: false
    highlight: tango
    fontsize: 12
    fig_caption: false
    toc: yes
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    theme: spacelab
params:
  mode: "interactive"
---

# Global Projections and Mitigation: MACC Curves

```{r,echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE, fig.align = "center", fig.width = 10, fig.height = 7)
```


```{r cars}
library(targets)
library(tarchetypes)
source("packages.R")

tar_source()
```


```{r pressure}
tar_load(clean_macc_2024)#,
         #combined_sources)
```


```{r, eval=FALSE}
emis_df <- emis_df %>%
  mutate(source = case_when(source %in% c("Aluminum Production","Magnesium Production") ~ "Metals",
                            source %in% c("Semiconductor Manufacturing",
                                          "Photovoltaic Cell Manufacturing",
                                          "Flat Panel Display Manufacturing") ~ "Electronics",
                            source %in% c("Aerosols",
                                          "Fire Protection",
                                          "Foams Mfg, Use, and Disposal",
                                          "Solvent Use",
                                          "Refrigeration and Air Conditioning") ~ "Substitutes for Ozone-Depleting Substances",
                            TRUE ~ source))


# DO renaming
# "NF3 Etching" - Combustion-Wet POU Abatement: FPD NF3 Etch
# "SF6 Cleaning" - Combustion-Wet POU Abatement: FPD SF6 Clean 
# "NF3 Cleaning" - Combustion-Wet POU Abatement: FPD NF3 CLean 
# "SF6 Etching" - Combustion-Wet POU Abatement: FPD SF6 Etch
# 
# CoW 


data3 <- arrange(data2, date)

FPD <- MACC_01302025 %>% dplyr::filter(source == "FPD")

PV <- MACC_01302025 %>% 
  dplyr::filter(source == "PV") %>%
  arrange(p)

SEMI <- MACC_01302025 %>% 
  dplyr::filter(source == "SEMI") %>%
  arrange(p)

# https://stackoverflow.com/questions/9564489/read-all-files-in-a-folder-and-apply-a-function-to-each-data-frame

# https://federicovegetti.github.io/teaching/heidelberg_2018/lab/sst_lab_day2.html

```




```{r}
# 
# macc_bySource_gas(combined_sources,yearSelect=2030, priceMin = -400,priceMax=100,versionSelect=2024,gasSelect = methane,legendOFF=TRUE)
# 

```


# Global Mitigation Opportunities by Sector {.tabset}

## Agriculture {.tabset}


### Smooth

```{r}


macc_smooth(clean_macc_2024, sectorSelect = "AGRICULTURE")
macc_smooth(clean_macc_2024, sectorSelect = "AGRICULTURE", yearSelect = 2050)


```

### By Tech
```{r}


macc_byTech(clean_macc_2024, sectorSelect = "AGRICULTURE")
macc_byTech(clean_macc_2024, sectorSelect = "AGRICULTURE", yearSelect = 2050)


```


## Energy {.tabset}


### Smooth

```{r}
macc_smooth(clean_macc_2024, sectorSelect = "ENERGY")
macc_smooth(clean_macc_2024, sectorSelect = "ENERGY", yearSelect = 2050)

```

### By Tech


```{r}

macc_byTech(clean_macc_2024, sectorSelect = "ENERGY")
macc_byTech(clean_macc_2024, sectorSelect = "ENERGY", yearSelect = 2050)

```


## Industrial Processes {.tabset}

### Smooth

```{r}
macc_smooth(clean_macc_2024, sectorSelect = "INDUSTRIAL")
macc_smooth(clean_macc_2024, sectorSelect = "INDUSTRIAL", yearSelect = 2050)

```

### By Tech


```{r}
macc_byTech(clean_macc_2024, sectorSelect = "INDUSTRIAL")
macc_byTech(clean_macc_2024, sectorSelect = "INDUSTRIAL", yearSelect = 2050)


```


## Waste {.tabset}



### Smooth

```{r}
macc_smooth(clean_macc_2024, sectorSelect = "WASTE")
macc_smooth(clean_macc_2024, sectorSelect = "WASTE", yearSelect = 2050)

```


### By Tech


```{r}
macc_byTech(clean_macc_2024, sectorSelect = "WASTE")
macc_byTech(clean_macc_2024, sectorSelect = "WASTE", yearSelect = 2050)

```


# Global Mitigation Opportunities by Source {.tabset}

## Gas {.tabset}



### Smooth

```{r}
macc_smooth(clean_macc_2024, sourceSelect = "GAS")
macc_smooth(clean_macc_2024, sourceSelect = "GAS", yearSelect = 2050)

```


### By Tech


```{r}
macc_byTech(clean_macc_2024, sectorSelect = "GAS")
macc_byTech(clean_macc_2024, sectorSelect = "GAS", yearSelect = 2050)

```



## Coal {.tabset}



### Smooth

```{r}
macc_smooth(clean_macc_2024, sourceSelect = "COL")
macc_smooth(clean_macc_2024, sourceSelect = "COL", yearSelect = 2050)

```


### By Tech


```{r}
macc_byTech(clean_macc_2024, sectorSelect = "COL")
macc_byTech(clean_macc_2024, sectorSelect = "COL", yearSelect = 2050)

```


## Landfill {.tabset}



### Smooth

```{r}
macc_smooth(clean_macc_2024, sourceSelect = "LAN")
macc_smooth(clean_macc_2024, sourceSelect = "LAN", yearSelect = 2050)

```


### By Tech


```{r}
macc_byTech(clean_macc_2024, sectorSelect = "LAN")
macc_byTech(clean_macc_2024, sectorSelect = "LAN", yearSelect = 2050)

```

## Wastewater {.tabset}


### Smooth

```{r}
macc_smooth(clean_macc_2024, sourceSelect = "WWR")
macc_smooth(clean_macc_2024, sourceSelect = "WWR", yearSelect = 2050)

```


### By Tech


```{r}
macc_byTech(clean_macc_2024, sectorSelect = "WWR")
macc_byTech(clean_macc_2024, sectorSelect = "WWR", yearSelect = 2050)

```
