---
pagetitle: "2024 Domestic Non-CO2 Report: MACC Curves "
output:
  html_document:
    number_sections: false
    highlight: tango
    fontsize: 12
    fig_caption: false
    toc: yes
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    theme: spacelab
params:
  mode: "interactive"
---



```{r,echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "show", warning = FALSE, message = FALSE, error = FALSE, fig.align = "center", fig.width = 10, fig.height = 7)
```


```{r cars}
library(targets)
library(tarchetypes)
source("packages.R")
tar_source()
```


```{r pressure}
tar_load(current_data)#,
         #combined_sources)
```


```{r, eval=FALSE}
emis_df <- emis_df %>%
  mutate(source = case_when(source %in% c("Aluminum Production","Magnesium Production") ~ "Metals",
                            source %in% c("Semiconductor Manufacturing",
                                          "Photovoltaic Cell Manufacturing",
                                          "Flat Panel Display Manufacturing") ~ "Electronics",
                            source %in% c("Aerosols",
                                          "Fire Protection",
                                          "Foams Mfg, Use, and Disposal",
                                          "Solvent Use",
                                          "Refrigeration and Air Conditioning") ~ "Substitutes for Ozone-Depleting Substances",
                            TRUE ~ source))



current_data <- current_data %>%
  mutate(source = case_when(source %in% c("AL","MG") ~ "Metals",
                            source %in% c("SEMI") ~ "Electronics",
                            source %in% c("AERO",
                                          "FIRE",
                                          "RAC") ~ "ODS-Subs",
                            TRUE ~ source))

# DO renaming
# "NF3 Etching" - Combustion-Wet POU Abatement: FPD NF3 Etch
# "SF6 Cleaning" - Combustion-Wet POU Abatement: FPD SF6 Clean 
# "NF3 Cleaning" - Combustion-Wet POU Abatement: FPD NF3 CLean 
# "SF6 Etching" - Combustion-Wet POU Abatement: FPD SF6 Etch
# 
# CoW 


#data3 <- arrange(data2, date)

# FPD <- MACC_01302025 %>% dplyr::filter(source == "FPD")
# 
# PV <- MACC_01302025 %>% 
#   dplyr::filter(source == "PV") %>%
#   arrange(p)
# 
# SEMI <- MACC_01302025 %>% 
#   dplyr::filter(source == "SEMI") %>%
#   arrange(p)

# https://stackoverflow.com/questions/9564489/read-all-files-in-a-folder-and-apply-a-function-to-each-data-frame

# https://federicovegetti.github.io/teaching/heidelberg_2018/lab/sst_lab_day2.html

```




```{r}
# 
# macc_bySource_gas(combined_sources,yearSelect=2030, priceMin = -400,priceMax=100,versionSelect=2024,gasSelect = methane,legendOFF=TRUE)
# 

```


# State-level Mitigation Opportunities: Sector Summary


```{r}

# by sector
summary_stats_sector <- current_data %>%
  mutate(max_100_q = case_when(p <=100 ~ q_total,
                               TRUE ~ 0)) %>%
  group_by(sector, year) %>%
  summarise(mitigation = sum(q_total),
            "mitigation up to $100" = sum(max_100_q)) %>%
  dplyr::filter(year %in% c(2030, 2050))

# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
mit_by_sector_summary <- kbl(summary_stats_sector, digits = 1) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

mit_by_sector_summary

```


# State-level Mitigation Opportunities by Sector {.tabset}

## Agriculture {.tabset}


### Smooth

```{r}


macc_smooth_updated(current_data, sectorSelect = "AGRICULTURE", splitFig = TRUE)
macc_smooth_updated(current_data, sectorSelect = "AGRICULTURE", yearSelect = 2050, splitFig = TRUE)


```

### By Tech
```{r}


macc_byTech_updated(current_data, sectorSelect = "AGRICULTURE", splitFig = TRUE)
macc_byTech_updated(current_data, sectorSelect = "AGRICULTURE", yearSelect = 2050, splitFig = TRUE)


```


## Energy {.tabset}


### Smooth

```{r}
macc_smooth_updated(current_data, sectorSelect = "ENERGY")
macc_smooth_updated(current_data, sectorSelect = "ENERGY", yearSelect = 2050)

```

### By Tech


```{r}

macc_byTech_updated(current_data, sectorSelect = "ENERGY")
macc_byTech_updated(current_data, sectorSelect = "ENERGY", yearSelect = 2050)

```


## Industrial Processes {.tabset}

### Smooth

```{r}
macc_smooth_updated(current_data, sectorSelect = "INDUSTRIAL")
macc_smooth_updated(current_data, sectorSelect = "INDUSTRIAL", yearSelect = 2050)

```

### By Tech


```{r}
macc_byTech_updated(current_data, sectorSelect = "INDUSTRIAL")
macc_byTech_updated(current_data, sectorSelect = "INDUSTRIAL", yearSelect = 2050)


```


## Waste {.tabset}



### Smooth

```{r}
macc_smooth_updated(current_data, sectorSelect = "WASTE")
macc_smooth_updated(current_data, sectorSelect = "WASTE", yearSelect = 2050)

```


### By Tech


```{r}
macc_byTech_updated(current_data, sectorSelect = "WASTE")
macc_byTech_updated(current_data, sectorSelect = "WASTE", yearSelect = 2050)

```

# State-level Mitigation Opportunities: Source Summary
```{r}
# by source
summary_stats_source <- current_data %>%
  mutate(max_100_q = case_when(p <=100 ~ q_total,
                               TRUE ~ 0)) %>%
  group_by(source, year) %>%
  summarise("total mitigation" = sum(q_total),
            "mitigation up to $100" = sum(max_100_q)) %>%
  dplyr::filter(year %in% c(2030, 2050))

# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
mit_by_source_summary <- kbl(summary_stats_source, digits = 1) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

mit_by_source_summary

```


# State-level Mitigation Opportunities by Source {.tabset}

## Agriculture {.tabset}

### Livestock {.tabset}

#### Smooth

```{r}
macc_smooth_updated(current_data, sourceSelect = "LIVE", splitFig = TRUE)
macc_smooth_updated(current_data, sourceSelect = "LIVE", yearSelect = 2050, splitFig = TRUE)

```


#### By Tech


```{r}
macc_byTech_updated(current_data, sourceSelect = "LIVE", splitFig = TRUE)
macc_byTech_updated(current_data, sourceSelect = "LIVE", yearSelect = 2050, splitFig = TRUE)

```



### Croplands {.tabset}

#### Smooth

```{r}
macc_smooth_updated(current_data, sourceSelect = "CROP", splitFig = TRUE)
macc_smooth_updated(current_data, sourceSelect = "CROP", yearSelect = 2050, splitFig = TRUE)

```


#### By Tech


```{r}
macc_byTech_updated(current_data, sourceSelect = "CROP", splitFig = TRUE)
macc_byTech_updated(current_data, sourceSelect = "CROP", yearSelect = 2050, splitFig = TRUE)

```

### Rice cultivation {.tabset}

#### Smooth

```{r}
macc_smooth_updated(current_data, sourceSelect = "RICE", splitFig = TRUE)
macc_smooth_updated(current_data, sourceSelect = "RICE", yearSelect = 2050, splitFig = TRUE)

```


#### By Tech


```{r}
macc_byTech_updated(current_data, sourceSelect = "RICE", splitFig = TRUE)
macc_byTech_updated(current_data, sourceSelect = "RICE", yearSelect = 2050, splitFig = TRUE)

```


## Energy {.tabset}

### Gas {.tabset}

#### Smooth

```{r}
macc_smooth_updated(current_data, sourceSelect = "GAS")
macc_smooth_updated(current_data, sourceSelect = "GAS", yearSelect = 2050)

```


#### By Tech


```{r}
macc_byTech_updated(current_data, sourceSelect = "GAS")
macc_byTech_updated(current_data, sourceSelect = "GAS", yearSelect = 2050)

```



### Coal {.tabset}

#### Smooth

```{r}
macc_smooth_updated(current_data, sourceSelect = "COL")
macc_smooth_updated(current_data, sourceSelect = "COL", yearSelect = 2050)

```


#### By Tech


```{r}
macc_byTech_updated(current_data, sourceSelect = "COL")
macc_byTech_updated(current_data, sourceSelect = "COL", yearSelect = 2050)

```


## Industrial Process {.tabset}

### EPS {.tabset}

#### Smooth

```{r}
macc_smooth_updated(current_data, sourceSelect = "EPS")
macc_smooth_updated(current_data, sourceSelect = "EPS", yearSelect = 2050)

```


#### By Tech


```{r}
macc_byTech_updated(current_data, sourceSelect = "EPS")
macc_byTech_updated(current_data, sourceSelect = "EPS", yearSelect = 2050)

```



### NAA Production {.tabset}

#### Smooth

```{r}
macc_smooth_updated(current_data, sourceSelect = "NAA")
macc_smooth_updated(current_data, sourceSelect = "NAA", yearSelect = 2050)

```


#### By Tech


```{r}
macc_byTech_updated(current_data, sourceSelect = "NAA")
macc_byTech_updated(current_data, sourceSelect = "NAA", yearSelect = 2050)

```

### Metals {.tabset}

#### Smooth

```{r}
macc_smooth_updated(current_data, sourceSelect = "Metals")
macc_smooth_updated(current_data, sourceSelect = "Metals", yearSelect = 2050)

```


#### By Tech


```{r}
macc_byTech_updated(current_data, sourceSelect = "Metals")
macc_byTech_updated(current_data, sourceSelect = "Metals", yearSelect = 2050)

```


### ODS-Subs {.tabset}

#### Smooth

```{r}
macc_smooth_updated(current_data, sourceSelect = "ODS-Subs")
macc_smooth_updated(current_data, sourceSelect = "ODS-Subs", yearSelect = 2050)

```


#### By Tech


```{r}
macc_byTech_updated(current_data, sourceSelect = "ODS-Subs")
macc_byTech_updated(current_data, sourceSelect = "ODS-Subs", yearSelect = 2050)

```

### Electronics {.tabset}

#### Smooth

```{r}
macc_smooth_updated(current_data, sourceSelect = "Electronics")
macc_smooth_updated(current_data, sourceSelect = "Electronics", yearSelect = 2050)

```


#### By Tech


```{r}
macc_byTech_updated(current_data, sourceSelect = "Electronics")
macc_byTech_updated(current_data, sourceSelect = "Electronics", yearSelect = 2050)

```


## Waste {.tabset}

### Landfill {.tabset}

#### Smooth

```{r}
macc_smooth_updated(current_data, sourceSelect = "LAN")
macc_smooth_updated(current_data, sourceSelect = "LAN", yearSelect = 2050)

```


#### By Tech


```{r}
macc_byTech_updated(current_data, sourceSelect = "LAN")
macc_byTech_updated(current_data, sourceSelect = "LAN", yearSelect = 2050)

```

### Wastewater {.tabset}


#### Smooth

```{r}
macc_smooth_updated(current_data, sourceSelect = "WWR")
macc_smooth_updated(current_data, sourceSelect = "WWR", yearSelect = 2050)

```


#### By Tech


```{r}
macc_byTech_updated(current_data, sourceSelect = "WWR")
macc_byTech_updated(current_data, sourceSelect = "WWR", yearSelect = 2050)

```
